\documentclass[addpoints,11pt]{exam}

\usepackage{alltt}
\usepackage[margin=1in]{geometry}   % set up margins
\usepackage[T1]{fontenc}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{enumerate}              % fancy enumerate
\usepackage{amsmath}                % used for \eqref{} in this document
\usepackage{amsthm}
\theoremstyle{definition}
\newtheorem{exmp}{Example}[section]
\usepackage{verbatim}               % useful for \begin{comment} and \end{comment}
\usepackage{eurosym}                % used for euro symbol
\usepackage{caption} 
\usepackage{graphicx}
\usepackage{threeparttable}
\graphicspath{{Figures/}}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{color}
\usepackage{float}
\usepackage{amssymb}
\usepackage{sgamevar}
\usepackage{sgame}
\usepackage[colorlinks=true]{hyperref}
\hypersetup{colorlinks=true, citecolor=ForestGreen, linkcolor=BlueViolet, urlcolor=Magenta}

\usepackage{array}
\newcolumntype{H}{@{}>{\lrbox0}l<{\endlrbox}}


%Solutions or nah (blank next two lines out for no solutions, unblank #3)
\printanswers
\newcommand{\dd}[1]{{\textbf{\textcolor{red}{#1}}}}
\newcommand{\ddp}[1]{\par {\textcolor{ForestGreen}{#1}}}

%\newcommand{\dd}[1]{}  
%\newcommand{\ddp}[1]{}

\setlength\parindent{0pt}
\unframedsolutions
\SolutionEmphasis{\color{red}}
\CorrectChoiceEmphasis{\color{red}}
\renewcommand{\choicelabel}{(\alph{choice})}
\newcommand{\blank}[0]{\underline{\hspace{3cm}}}
\pointformat{\bfseries[\thepoints]}
\pointpoints{pt}{pts}
\pointsinrightmargin

\begin{document}
	
	
	\title{\textbf{Exam 1 Study Guide} \\ \vspace{2 mm} {\large ECON 380} \\ \large{UNC Chapel Hill}}
	\date{}
	\maketitle
	
Stuff to know for exam 1:

\subsection*{Labor Force Accounting \& Unemployment}

\begin{enumerate}
	\item How to classify individuals - E, U, O, or not in P
	\item What are discouraged workers? Marginally attached workers?
	\item How to compute the LFPR
	\item How to compute the unemployment rate
	\item What are the major issues with using the unemployment rate?
	\item What are the different types of unemployment? 
	\item What policies might be most effective at combating different unemployment types? 
\end{enumerate}

\subsection*{Neoclassical Model of Labor Supply}

\begin{enumerate}
	\item Properties of indifference curves
	\item What do $MU_L$ and $MU_C$ measure?
	\item What is $MRS_{L,C}$ in words? Graphically?
	\item How to write the equation for an individual's budget constraint and how to graph a budget constraint (CHARLIE)
	\item What is the price of leisure? 
	\item How do changes in (i) non-labor income and (ii) wages affect the budget constraint?
	\item How does a worker choose the optimal number of work hours? Don't need to know how to algebraically solve, just the condition and how to show graphically.
	\item What's the intuition behind the tangency condition? How should a worker reallocate his bundle if $MRS_{L,C} < w$? If $MRS_{L,C} > w$? (e.g., exam 1 question)
	\item How do changes in non-labor income affect the hours-worked decision if leisure is income normal?
	\item How do changes in the wage rate affect the hours-worked decision? Is the overall impact unambiguous? 
	\item What happens to hours-worked if the income effect dominates the substitution effect? What if the substitution effect dominates the income effect? What do the graphs look like for each case?
	\item What is the endowment point? 
	\item What is the reservation wage (in words)? How to calculate it?
	\item How do changes in non-labor income affect the reservation wage? Changes in the wage rate?
	\item Model predictions under (i) AFDC/TANF and (ii) the Earned Income Tax Credit
\end{enumerate}

\subsection*{Labor Demand}

\begin{enumerate}
	\item What do we assume is the goal of a firm?
	\item What is the condition to find the optimal number of workers to hire in the short-run? 
	\item Solving for optimal number of workers to hire in SR (e.g., HW and exam questions)
	\item Condition to optimally allocate labor and capital in the LR.
	\item How to reallocate labor and capital given $r$, $w$, and $MRTS$. Know how to explain why the reallocation is more efficient
	\item Relationship between short-run and long-run demand elasticity? Why?
	\item Effects of minimum wage in a competitive labor market. How unemployment and employment relate to elasticity of supply and demand.
	\item How and why short-run vs. long-run effects of minimum wage likely differ
\end{enumerate}

\end{document}